---
title: "Qmd_Example"
format: html
---

# Big heading

## Medium heading

### Small heading

This is an example of a .qmd file. We can define code chunks by using three grave accents, followed by curly brackets around r. A code chunk looks like this;

```{r}
x = c(1,2,3)
y = c(2,4,6)
```

If we write code that produces output, such as this:

```{r}
plot(x,y)
```

The output will appear inline in the rendered document right after the code chunk. If you don’t want the code of a particular code chunk to appear in the final document, but still want to show the output (e.g. a plot), then you can include the **option** `echo: FALSE` in the first line of the code chunk, with option lines designated with a pound and a pipe `#|` at the start of the line:

```{r}
#| echo: false
plot(x,y)
```

There are plenty of other code chunk instructions you can include in the curly braces to customize your `.qmd` file.

---

Bulleted lists:

My family's fave pizza toppings:

-   pineapple
-   bacon

---

My pet's in order of how much mischievous they are:

1.  Clyde (dog-cat)
2.  Bonnie (cat)
3.  Nana (dog-cat)

---

I can italicize text like *this* or like *this* and I can embolden text like **this** or like **this**

---

superscript^23^ and subscript~2~